Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Figures updating

```{r libraries}
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(MetBrewer)
```

@@

>>>>

```{r libraries}
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(MetBrewer)
library(stringr)
```

@@

# Figure 3
Introduce the numerical estimation thing with the simple lomax:

```{r}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)", title = "Lomax Parameter Space") +
  theme_bw() +
  theme(legend.position = "bottom")
